Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2019-01-13 notes-duality/dual-of-loss.tex
typo fix in notes. bo@nyc

\documentclass[12pt]{article}
\usepackage{amsmath,amsth,amsfonts,amssymb}

@@

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,amsfonts,amssymb}

\DeclareMathOperator*{\argmin}{\textrm{argmin}}

@@

\break

\section{Added by Bo 2019-01-11}

\subsection{Convex loss functions and duality}
For each outcome $j=1,\dots,k$, let $\ell_j(x)$ be the loss function.

\paragraph{Scaling}
Given positive $p_j$, note that $(p_j \ell_j)^*$ is the following object:
\begin{enumerate}
  \item Let $F_j^*$ be the epigraph of $\ell_j^*$, a convex set.
  \item Scale the set $F_j^*$ by $p_j$.
  \item This is the epigraph of $(p_j \ell_j)^*$.
\end{enumerate}

\paragraph{Summing}
Given convex $f,g$, note that $(f+g)^*$ is the following object:
\begin{enumerate}
  \item Take the epigraphs $F^*,G^*$ of the functions $f^*,g^*$.
  \item Form the Minkowski sum $F^* + G^*$.
  \item This is the epigraph of $(f+g)^*$.
\end{enumerate}

\paragraph{Convex combination.}
Let $\ell(x;p) = \sum_{j=1}^k p_j \ell_j(x)$.
By the above, we know that (taking the conjugate with respect to the $x$ argument only) $\ell^*(x^*;p)$ is the following object:
\begin{enumerate}
  \item Let $F_j^*$ be the epigraph of $\ell_j^*$.
  \item Form the Minkowski combination $F^*(p) := \sum_{j=1}^k p_j F_j^*$.
  \item This is the epigraph of $\ell^*(x^*;p)$.
\end{enumerate}
The combinatorial properties of $F^*(p)$ don't depend on $p$, as long as each $p_j$ is strictly positive!

\subsection{Optimal reports}
Now $x \in \argmin_x \ell(x;p)$ if and only if $0 \in \partial \ell(x;p)$ if and only if $x \in \partial \ell^*(0 ; p)$.

Fixing $x$
